Placeholder Title... Something About Delegating Quantum Computations

### 2019-09-11 delegations.tex
Make editorial change
Write about security

\begin{definition}
	A quantum delegation protocol is \emph{secure} if a malicious prover cannot learn the input or the output of the computation. In particular, security notions such as \emph{CPA} can be applied here. (TODO Just define CPA right away since there are no other security notions around here)
\end{definition}

@@

In \cite{mahadev_delegation}, a verifiable scheme is proposed. In \cite{mahadev_qfhe}, a secure scheme is proposed. (TODO just make this CPA or whatever it actually is...) We propose a verifiable scheme with long output which can also be made secure.

@@

We start by constructing a verifiable long output scheme. Then, we encrypt the scheme as given in \cite{mahadev_delegation} to achieve security. That is, we first encrypt the circuit. Then TODO it's not immediately obvious that this works. This isn't purely a circuit anymore, but we also have classical data and evaluation key now.

>>>>

\begin{definition}
	A quantum delegation protocol is \emph{CPA-secure} if both the input and output of the circuit are CPA-secure as ciphertexts. In this case, the scheme should be seen as a homomorphic encryption scheme.
\end{definition}

@@

In \cite{mahadev_delegation}, a verifiable scheme is proposed. In \cite{mahadev_qfhe}, a secure scheme is proposed. (TODO just make this CPA or whatever it actually is...)

@@

We propose a verifiable scheme with long output which can also be made secure. We start by constructing a verifiable long output scheme. Then, we use \cite{mahadev_delegation} to achieve security. That is, we the techniques in \cite{mahadev_delegation} to encrypt the circuit and the input. We also tack on the evaluation key as extra input, so the entire computation can still be encoded as a single circuit.
